Methods to prioritise pop-up active transport infrastructure and their application in a national cycleway prioritisation tool

### 2020-06-22 article.Rmd

1. Measures such as point closures or contraflow cycle lanes, which can be used to promote 'filtered permeability', a strategy in which street networks are redesigned so that routes for cyclists are faster and more direct than routes for drivers. An example of this is  [shown](https://twitter.com/TowerHamletsNow/status/1257564043856019458) in [Tower Hamlets].
2. Measures to close roads entirely to motor traffic or to particular classes of vehicle, either permanently or at certain times of day, as in New York's 'Open Streets' scheme [@litman_pandemicresilient_2020].
3. Measures to reallocate space on wide roads to create new cycleways or to widen pavements [@orsman_covid_2020].
<!-- interventions to prevent through traffic, with interventions as part of Salford's ['Liveable Streets' project](https://salfordliveablestreets.commonplace.is/) being a prominent example  -->
<!-- (see [here](https://twitter.com/CatrionaSwanson/status/1258322956595453952) for a photo illustrating this type of intervention) -->

@@

Roads are classified by speed limit because this has been shown to be a key factor associated with the incidence of severe injuries and fatalities of cyclists [@chen_built_2016], with odds of cyclist injury on 20 mph roads in London found to be 21% lower than on 30 mph roads [@aldred_cycling_2018]. 
Therefore the suitability of roads for cycle infrastructure, the preferred degree of physical segregation, or the necessity to reduce traffic speeds could all be influenced by current speed limits.

```{r t1, results='asis', fig.cap="Summary of the road segment dataset for Leeds.", message=FALSE}
rj_leeds = readRDS("r_main_leeds.Rds")
# See https://cran.r-project.org/web/packages/qwraps2/vignettes/summary-statistics.html
# rj_leeds %>%
#   st_drop_geometry() %>%
#   mutate(`width (m)` = width) %>%
#   select(name, highway_type, maxspeed, cycling_potential, `width (m)`, n_lanes) %>%
#   group_by(maxspeed) %>% 
#   # qwraps2::summary_table()
#   table1::table1(~ highway_type + cycling_potential + `width (m)` + n_lanes | maxspeed, data = .)
t1 = readr::read_csv("input-data/t1.csv")[-1]
n = c(
  "",
  "4777",
  "19241",
  "3105",
  "27123"
)
names(n) = names(t1)
t2 = rbind(n, t1)
names(t2)[1] = ""
# t1
t2 %>% 
  kableExtra::kable(caption = "Summary of the road segment dataset for Leeds.",
    # escape = FALSE,
    booktabs = TRUE,
    # col.names = kableExtra::linebreak(names(t1)),
    format = "latex"
    ) %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::pack_rows("N. observations", 1, 2) %>% 
  kableExtra::pack_rows("Highway type", 2, 13) %>% 
  kableExtra::pack_rows("Cycling potential", 14, 15) %>%  
  kableExtra::pack_rows("Width (m)", 16, 18) %>% 
  kableExtra::pack_rows("N. lanes", 19, 22)

>>>>

1. Measures such as point closures or contraflow cycle lanes, which can be used to promote 'filtered permeability', a strategy in which street networks are redesigned so that routes for cyclists are faster and more direct than routes for drivers. An example of this is  [shown](https://twitter.com/TowerHamletsNow/status/1257564043856019458) in [Tower Hamlets].
2. Measures to close roads entirely to cars, either permanently or at certain times of day, as in New York's 'Open Streets' scheme [@litman_pandemicresilient_2020].
3. Measures to reallocate space on wide roads to create new cycleways or to widen pavements [@orsman_covid_2020].
<!-- interventions to prevent through traffic, with interventions as part of Salford's ['Liveable Streets' project](https://salfordliveablestreets.commonplace.is/) being a prominent example  -->
<!-- (see [here](https://twitter.com/CatrionaSwanson/status/1258322956595453952) for a photo illustrating this type of intervention) -->

@@

Roads are classified by speed limit because this has been shown to be a key factor associated with the incidence of severe injuries and fatalities of cyclists [@chen_built_2016], with odds of cyclist injury on 20 mph (32.2 kmph) roads in London found to be 21% lower than on 30 mph (48.3 kmph) roads [@aldred_cycling_2018]. 
Therefore the suitability of roads for cycle infrastructure, the preferred degree of physical segregation, or the necessity to reduce traffic speeds could all be influenced by current speed limits.

```{r t1, results='asis', message=FALSE}
rj_leeds = readRDS("r_main_leeds.Rds")
# See https://cran.r-project.org/web/packages/qwraps2/vignettes/summary-statistics.html
# rj_leeds %>%
#   st_drop_geometry() %>%
#   mutate(`width (m)` = width) %>%
#   select(name, highway_type, maxspeed, cycling_potential, `width (m)`, n_lanes) %>%
#   group_by(maxspeed) %>% 
#   # qwraps2::summary_table()
#   table1::table1(~ highway_type + cycling_potential + `width (m)` + n_lanes | maxspeed, data = .)
t1 = readr::read_csv("input-data/t1.csv")[-1]
n = c(
  "",
  "4777",
  "19241",
  "3105",
  "27123"
)
names(n) = names(t1)
t2 = rbind(n, t1)
names(t2)[1] = ""
# t1
t2 %>% 
  kableExtra::kable(caption = "Summary of the road segment dataset for Leeds. Units of speed are in miles per hour (mph), with 20, 30 and 40 mph representing 32, 48 and 64 kilometers per hour respectively.",
    # escape = FALSE,
    booktabs = TRUE,
    # col.names = kableExtra::linebreak(names(t1)),
    format = "latex"
    ) %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::pack_rows("N. observations", 1, 2) %>% 
  kableExtra::pack_rows("Highway type", 2, 13) %>% 
  kableExtra::pack_rows("Cycling potential", 14, 15) %>%  
  kableExtra::pack_rows("Width (m)", 16, 18) %>% 
  kableExtra::pack_rows("N. lanes", 19, 22)
